---
title: "README"
author: "JIAYI HONG"
date: "9/21/2021"
output: github_document
---


```{r}
library(dplyr)

# install.packages("nycflights13")
library(nycflights13)
library(ggplot2)
library(ggfortify)
```

8,255 flights have a missing dep_time. Additionally, 8255 have a missing dep_delay, 8713 have a missing arr_time, 9430 have a missing arr_delay, and 9430 have a missing air_time. These rows might represent flights that were canceled or had unscheduled landing at another airport or data is lost due to error. 

```{r}
filter(flights, is.na(dep_time))

summary(flights)
```


```{r}
mutate(flights,
       dep_time = (dep_time %/% 100) * 60 + (dep_time %% 100),
       sched_dep_time = (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100))
```

```{r}
library(lubridate)
flights %>%
  mutate(dep_date = make_datetime(year, month, day)) %>%
  group_by(dep_date) %>%
  summarise(canceled_prop = sum(is.na(dep_time)) / n(),
         mean_dep_delay = mean(dep_delay,na.rm=T),
         mean_arr_delay = mean(arr_delay,na.rm=T)) %>%
  
  ggplot(aes(x = canceled_prop, alpha = 0.5)) +
  geom_point(aes(y= mean_dep_delay, col = "Dep Delay")) +
  geom_point(aes(y = mean_arr_delay, col = "Arr Delay"))+
  labs(y = "Average Delay (minutes)", x = "Proportion of Canceled Flight")+
  theme(legend.position = "bottom")+
  guides(alpha = F)
```
  
There is roughly a linear relationship between the proportion of canceled flights and the average delay


